Verification of a Deterministic Random Bits Generator

### 2015-12-23 paper/paper.tex
use section symbol instead of the word section

The state machine representation of HMAC was created for this project. \cite{hmac} describes the previous verification effort on HMAC, but it represented HMAC in a more low-level format. See section \ref{oldhmac} for more details.

@@

This representation works in the sense that the verification of the \stdtitle{OpenSSL} functions went through. Unfortunately, for clients of this API specification, this representation is often not good enough. The biggest issue is that this representation is too low-level; it does not keep track of the key. Upon notified of this issue, the developers of the HMAC API specification were quickly able to provide a more abstract representation of the HMAC state, leading to the state machine representation shown earlier in section \ref{hmac_interface}. The core of the verification code did not need to be changed, with some book-keeping added at the ends of translate between the new, more abstract representation to the more low-level implementation. While this issue was easily fixed, it would have been very hard to discover this issue without actually being clients of the API specification. This highlights the importance of having being the first client of the HMAC API specification.

@@

As previously mentioned in section \ref{hmac_interface}, previous verification efforts on HMAC and SHA are done on \stdtitle{OpenSSL}. Therefore, the \stdtitle{mbedTLS} DRBG implementation must somehow call into the \stdtitle{OpenSSL} HMAC implementation, so that the API specifications for HMAC can be used. To do this, I wrote a thin wrapper around the \stdtitle{mbedTLS} message digest interface. In this section, I show exactly how I did that.

>>>>

The state machine representation of HMAC was created for this project. \cite{hmac} describes the previous verification effort on HMAC, but it represented HMAC in a more low-level format. See \S \ref{oldhmac} for more details.

@@

This representation works in the sense that the verification of the \stdtitle{OpenSSL} functions went through. Unfortunately, for clients of this API specification, this representation is often not good enough. The biggest issue is that this representation is too low-level; it does not keep track of the key. Upon notified of this issue, the developers of the HMAC API specification were quickly able to provide a more abstract representation of the HMAC state, leading to the state machine representation shown earlier in \S \ref{hmac_interface}. The core of the verification code did not need to be changed, with some book-keeping added at the ends of translate between the new, more abstract representation to the more low-level implementation. While this issue was easily fixed, it would have been very hard to discover this issue without actually being clients of the API specification. This highlights the importance of having being the first client of the HMAC API specification.

@@

As previously mentioned in \S \ref{hmac_interface}, previous verification efforts on HMAC and SHA are done on \stdtitle{OpenSSL}. Therefore, the \stdtitle{mbedTLS} DRBG implementation must somehow call into the \stdtitle{OpenSSL} HMAC implementation, so that the API specifications for HMAC can be used. To do this, I wrote a thin wrapper around the \stdtitle{mbedTLS} message digest interface. In this section, I show exactly how I did that.
